Whittaker Models for Real Groups

### 2024-06-12 whittaker.tex
Tinkering

This restricts to an isomorphism $\N\simeq \N^*$. Although this isomorphism depends on the choice of form,
the bijection on the level of $G$-orbits is canonical.

@@

In the $\theta$-picture we have an analogous construction. We may assume the form is orthogonal with respect to $\theta$.
Consequently the decomposition $\g=\mathfrak k+\s$ also gives $\g^*=\mathfrak k^*\oplus \s^*$, and this induces
a canonical bijection between $K$-orbits on $\s$ and on $\s^*$.

@@

Suppose $\pi$ is an irreducible $(\g,K)$-module.
Let $I_\pi$ be the annihlator of $\pi$ in the universal enveloping algebra.
Let $\AVann(\pi)\subset\N^*\subset \g^*$ be the associated variety of $I_\pi$.
This is the closure of a single complex nilpotent orbit $\O$
See \cite[Section 1, Theorem 4.7]{vogan_bowdoin}.

The associated variety of $\pi$, denoted $\AV(\pi)$, is a closed, $K$-invariant set in~$\s^*$; so it is a finite union of
nilpotent $K$-orbits on $\s^*$. See \cite[Section 5]{vogan_bowdoin}.

@@

We define the associated variety of a Hilbert space representations to be that of  its underlying $(\g,K)$-module.

>>>>

The identification $\g \simeq \g^\ast$ restricts to a bijection $\N\simeq \N^*$. Although this correspondence depends on the choice of form,
the induced bijection on the level of $G$-orbits is canonical.

@@

We may assume the chosen bilinear form on~$\g$ is $\theta$-invariant. In this case the identification between $\g=\mathfrak k+\s$ and $\g^*=\mathfrak k^*\oplus \s^*$ determines a $K$-equivariant  (but non-canonical) isomorphism between $\s$ and $\s^\ast$. This induces
a canonical bijection between $K$-orbits on $\s$ and on $\s^*$.

@@

Suppose $\pi$ is an irreducible $(\g,K)$-module.

The associated variety of $\pi$, denoted $\AV(\pi)$, is a closed, $K$-invariant set in~$\s^*$; so it is a finite union of
nilpotent $K$-orbits on $\s^*$. For the definition, and many properties, see \cite[Section 5]{vogan_bowdoin}.

A slightly different invariant is the associated variety of the annihilator. Let $I_\pi$ be the annihlator of $\pi$ in the universal enveloping algebra.
Let $\AVann(\pi)\subset\N^*\subset \g^*$ be the associated variety of $I_\pi$.
This is the closure of a single complex nilpotent orbit $\O$.
See \cite[Section 1, Theorem 4.7]{vogan_bowdoin}.

@@

We define the associated variety of a Hilbert space representation to be that of  its underlying $(\g,K)$-module.
